Project Protocol

### 2019-10-18 protocol.Rmd
changes

A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable called $collect$.

The accuracy of the choices for each display will be calculated as a proportion: 
$accuracy = number correct/number shown$.

@@

High efficiency occurs when a small amount of time is taken to evaluate each lineup.
This will be measured as the inverse of the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

The efficiency of the choices for each display will be calculated by the time taken as a fraction of the maximum time taken by all respondents to respond:
$efficiency = time taken/maximumtime taken$.

@@

@@

Design:
We will model the difference between the accuracy and efficiency when evaluating hexagon tile maps and geographic maps.

@@

Cofactors:
responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.

Interactions:

>>>>

A correct result occurs when the chosen plot matches the position of the real plot, this will be recorded in an additional binary variable; $1 = correct;~ 0 = incorrect$.

@@

High efficiency occurs when a small amount of time is taken to evaluate each lineup.
This will be measured as the numeric variable measuring the length of time taken to submit the answers to the evaluation of each line up.

@@

A multilevel linear model with be fitted to the data with elements as specified below.

@@

Main Effects:
Design, Trend

@@

Possible Interactions:
Design and Trend, Design and Difficulty, Design and Reason

Possible covariates:
Responses to the questions regarding the difficulty of making a choice and the reason for the choice of plot in the line up.
